---
title: "Introduction to R Programming"
author: "RealAnalytics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Representing Data using Data Structures 

An Overview: Vectors, Matrics and Arrays, Lists, Data Frames, Factors and Tables 
Why is this important? 

- Code errors are many times due data represented as an incorrect data structure
- As a more advanced R user, need to know when creating packages and deploying models etc. 

## Stories make everything easier to understand. Let's go with Harry Potter 

### Vectors 
Homogenous
- logical
- character
- integer
- numeric

```{r}
is_wizard_as_logical_var <- c(TRUE, TRUE, FALSE)
is.logical(is_wizard_as_logical_var)

creatures_as_character_var <- c("Skrewt", "Hippogriff")
is.character(creatures_as_character_var)

owls_as_integer_var <- c(1L, 6L, 10L)
is.integer(owls_as_integer_var)

house_points_as_numeric_var <- c(1000, 2000, 3000)
is.numeric(house_points_as_numeric_var)
```

Challenge: Represent your own variables as the different types of vectors

### Matrics and Arrays
Homogenous
```{r}
a <- matrix(1:6, ncol = 3, nrow = 2)
a
```
```{r}
b <- array(1:12, c(2, 3, 2))
b
```


### Lists 
Heterogenous
```{r}
hermione_subject_scores <- list(c("herbology","muggle studies"),c(95, 99))
hermione_subject_scores
```

```{r}
is.list(hermione_subject_scores)
```

### Data Frames
Heterogenous
```{r}
df <- data.frame(x = c(1,2,3,4), houses = c("gryffindor","slytherin", "ravenclaw","hufflepuff"))
str(df)
```


